Minutes Modelleren 25-05-2021

### 2021-06-17 Minutes/Minutes_Modelleren_4.8.tex

\begin{document}
\section*{Minutes Wednesday}
Aanwezig: Bart, Dyami, Severijn
Voorzitter: Dyami
Secretaris: Bart

@@

\subsection*{Planning}
\begin{itemize}
    \item First draft Pitch done before Thursday.
    \item Finish ILP implementation before Thursday.
\end{itemize}
\end{document}

>>>>

\begin{document}
\section*{Minutes Tuesday}
Aanwezig: Bart, Dyami, Severijn \\
Voorzitter: Dyami \\
Secretaris: Bart

@@

\subsection*{Planning}
\begin{itemize}
    \item First draft Pitch done before Thursday.
    \item Finish ILP implementation before Thursday.
\end{itemize}

\section*{Minutes Thursday}
Aanwezig: Iedereen \\
Voorzitter: Dyami \\ 
Secretaris: Bart \\

\subsection*{Discussed topics}
\begin{itemize}
    \item Discuss the received feedback on the draft report.
    \item Discuss the pitch made by Severijn
\end{itemize}

\subsection*{Decisions}
\begin{itemize}
    \item Report needs to be done by Tuesday so that we can discuss it by Thursday. 
\end{itemize}

\subsection*{Planning}
\begin{itemize}
    \item Incorporate feedback into report by Tuesday (Everyone)
    \item Add small data set results to report (Everyone)
    \item Finalize Pitch (Severijn)
    \item Expanded problem ILP implementation by tomorrow (Bart)
\end{itemize}
\end{document}
